LSOA domestic Electricty and Gas maps

### 2021-08-09 LSOA domestic Elec and Gas.Rmd
Changing files paths and title

---
title: "Solent region: Test Maps"
author: "Meghan Kinglsey-Walsh"
date: 'Last run at: `r Sys.time()`'
output:
  bookdown::html_document2:
    fig_caption: yes
    code_folding: hide
    number_sections: yes
    toc: yes
    toc_depth: 4
    toc_float: TRUE
  bookdown::pdf_document2:
    toc: yes
    fig_caption: yes
    number_sections: yes
  bookdown::word_document2: 
    fig_caption: yes
    number_sections: yes
    toc: yes
    toc_depth: 4
    fig_width: 5
---

@@

# Mapping the Lower Layer Super Output Area (LSOA)
## Mapping Domestic
### Mapping Electricity consumption
####2019
```{r Loading in the LSOA electricty consumption data}
#Electricty consumption data LSOA pre downloaded
inFile <-paste0(dataFolder, "energy/LSOA_ELEC_2019.csv")
lsoa_elecData <- readr::read_csv(inFile)
lsoa_elecData$LSOA11CD <- lsoa_elecData$`Lower Layer Super Output Area (LSOA) Code`
head(lsoa_elecData)
```

@@

### Mapping Gas
####2019
```{r Loading in the LSOA gas consumption data}
#Electricty consumption data LSOA pre downloaded
inFile <-paste0(dataFolder, "energy/LSOA_GAS_2019.csv")
lsoa_gasData <- readr::read_csv(inFile)
lsoa_gasData$LSOA11CD <- lsoa_gasData$`Lower Layer Super Output Area (LSOA) Code`
head(lsoa_gasData)
```

>>>>

---
title: "LSOA domestic Electricty and Gas maps"
author: "Meghan Kinglsey-Walsh"
date: 'Last run at: `r Sys.time()`'
output:
  bookdown::html_document2:
    fig_caption: yes
    code_folding: hide
    number_sections: yes
    toc: yes
    toc_depth: 4
    toc_float: TRUE
  bookdown::pdf_document2:
    toc: yes
    fig_caption: yes
    number_sections: yes
  bookdown::word_document2: 
    fig_caption: yes
    number_sections: yes
    toc: yes
    toc_depth: 4
    fig_width: 5
---

@@

# Mapping the Lower Layer Super Output Area (LSOA)
## Mapping Domestic
### Mapping Electricity consumption
####2019
```{r Loading in the LSOA electricty consumption data}
#Electricty consumption data LSOA pre downloaded
inFile <-paste0(dataFolder, "energy/electricity/LSOA Dom Elec csv/LSOA_ELEC_2019.csv")
lsoa_elecData <- readr::read_csv(inFile)
lsoa_elecData$LSOA11CD <- lsoa_elecData$`Lower Layer Super Output Area (LSOA) Code`
head(lsoa_elecData)
```

@@

### Mapping Gas
####2019
```{r Loading in the LSOA gas consumption data}
#Electricty consumption data LSOA pre downloaded
inFile <-paste0(dataFolder, "energy/gas/LSOA Gas csv/LSOA_GAS_2019.csv")
lsoa_gasData <- readr::read_csv(inFile)
lsoa_gasData$LSOA11CD <- lsoa_gasData$`Lower Layer Super Output Area (LSOA) Code`
head(lsoa_gasData)
```
